### 2016-05-04 hoist.tex
hoisting scalars past a call

>>>>

\section{Hoisting scalars}
Scalars are the easiest to hoist because we do not have to analyze for mem-refs. As long as all the
operands are available (which in SSA form we do, or may be there are chained dependencies), the scalar can
be hoisted. Care must be taken in case of hoisting scalars too far, as that may increase register pressure
and result in spills. For example hoisting a scalar past a call. In that case the call may result in
save and restore of the register the scalar may be defined to. In our current implementation
we do not hoist scalars past a call. Another way to mitigate this problem would be to
reinstantiate (rematerialize) the computation after a call (may be as a different pass).

\section{Hoisting calls}
Calls can be hoisted by value-numbering all the arguments. For safety we have to check that no other side-effects are there
between call and the hoisting point, just like loads and stores.

\section{Hoisting stores}
We need to value number the address and the value being stored.
